%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Stylish Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Stefano (http://stefano.italians.nl/archives/63)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% The two fonts used in this template: Adobe Garamond Pro and Gill Sans
% do not come with Windows by default. You will need to download them in
% order to get an output as in the preview PDF. Otherwise, change those 
% fonts to fonts that do come with Windows or comment out the lines to use 
% the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrlttr2}

\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbols
\usepackage[english]{babel} % Required to compile in Windows
\usepackage{hyperref}

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\defaultfontfeatures{Mapping=tex-text}
\setmainfont {Garamond} % Main document font
\setsansfont {Gill Sans} % Used in the from address line above the to address

\renewcommand{\normalsize}{\fontsize{12.5}{17}\selectfont} % Sets the font size and leading

%----------------------------------------------------------------------------------------
%  PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

\setkomavar{fromname}{David Fenko} % Your name
\setkomavar{fromaddress}{2332 N. Hamilton Ave \#1B\\Chicago, IL} % Your address
\setkomavar{fromphone}{(312) 342-6897} % Your phone number
\setkomavar{fromemail}{dfenko@fenkostan.com} % Your email address
\setkomavar{place}{} % City written before the date, put your city here if you want this
\setkomavar{signature}{David Fenko} % Your name as you want it to appear in the signature

% These are not used in this document, uncomment if you would like to use them and refer to them as \usekomavar{name}
%\setkomavar{fromfax}{+1 (1)23 456789} % Your fax number
%\setkomavar{fromurl}{http://troughnetwork.com} % Your personal website
%\setkomavar{frombank}{Postbank 9307157}

%----------------------------------------------------------------------------------------
%  HEADER SECTION
%----------------------------------------------------------------------------------------

\firsthead{
\centering
{\addfontfeature{LetterSpace=20.0}\fontsize{36}{36}\selectfont\scshape \usekomavar{fromname}}\\[5mm]
\fontsize{21}{21}\selectfont\scshape Senior Support Manager at Backstop Solutions Group} % Your current job title

%----------------------------------------------------------------------------------------
%  FOOTER SECTION
%----------------------------------------------------------------------------------------


\firstfoot{
\centering
\addfontfeature{LetterSpace=20.0}\scshape
{
\renewcommand{\\}{\ {\large\textperiodcentered}\ }
\usekomavar{fromaddress}
}\\
{\Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone} % If you want your fax number or website URL showing, add it here; you may need to play around with spacing
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% COVER LETTER CONTENTS
%----------------------------------------------------------------------------------------

\begin{letter}{ % Address of the company you are applying to
Hiring Team --- Wyzant\\
}

\opening{Dear Wyzant Hiring Team,}

I am reaching out to you in order to demonstrate my interest in the Product Manager position. I came across the opening while researching your firm after speaking with a friend who recently accepted a position with Wyzant. I have worked within the software industry for the last 5 years, wearing a variety of hats at a start-up, and I'm looking to apply that experience elsewhere.\\

My current role is the Senior Support Manager at Backstop Solutions Group. I am responsible for running multiple teams concerned with providing support to our client base. Our support role is less like a call center, instead opting to bring in bright individuals that can troubleshoot issues while still maintaining relationships. Given the role, my team takes on additional responsibilities, inclusive of logging development tickets and assisting in the prioritization of work. Personally, I have been responsible for managing development projects for support related features during my time at Backstop. Additionally, in order to better help provide input to the organizations Product Management team, I have taken the Foundations course offered by Pragmatic Marketing, and look forward to several of their other offerings.\\

Technically, I spend time at work combing through various databases to investigate data conditions within our own application or to work on valuing the effectiveness of the team that I manage. Using data collected from our systems through SQL in Excel, I have been able to help guide the growth of my team by providing an accurate picture of the current state of affairs. In addition to that, my current position is foremost a position based on accurate and tactful communication.\\

I would love to meet with your team to discuss my candidacy. A position such as this has been an ambition of mine most of my life. I am able to make myself available at your convenience, so please do not hesitiate to call me at (312) 342-6897 or email me at dfenko@fenkostan.com. Thank you for taking the time to consider my resume.\\

Sincerely yours, \\ \\
\usekomavar{signature}

%----------------------------------------------------------------------------------------

\end{letter}
\end{document}